Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
characteristics

The censor cannot sniff the content of communications or infer the existence of meek traffic 
from packet \emph{data}, 
since the communication is encrypted inside the TLS session, and we have devoted large efforts 
in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
the existence of meek traffic according to the \emph{metadata}, i.e. traffic characteristics. 
We studied a collection of traffic characteristics and evaluated their possibilities of becoming
the censor's interest. Specifically, we considered three characteristics: 1) payload length of
TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime. To collect 
the traffic trace of meek, we browsed the Alexa top 500 websites sequentially using the Tor Browser Bundle
and dumped the traffic trace from 
the network interface. We ensured only the browser can successfully access the network by setting
up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
obtained a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. We also
specifically extracted the traffic between LBL and Google. Since the trace only has packet headers, we 
cannot extract the domain information. However, the \texttt{TXT} DNS records of the domain 
\texttt{\_netblocks.google.com} shows the IP address blocks that belongs to Google. Therefore, we 
determine whether a flow is from or to Google by examining the address in the IP header. For this
study we are only interested in Google traffic, because the censor will be mostly likely to compare
suspected meek traffic with normal Google traffic. This part of the trace is 312 MB in size.

@@

Recall that we use browsers to handle HTTPS connections for meek in order to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistant TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

These browser techniques improve performance, but also lead to unexpected results. The censor may be aware of the 
deviation from the distribution of normal traffic. Additionally, the persistent connection itself can be a problem.
We thus investigated other related characteristics.

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth, angle=270]{figs/connections-google.eps}
\caption{Histogram of each user's connections in the 10-minute window}
\label{fig:connections}
\end{figure}
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figs/conns.eps}
\caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
\label{fig:len:meek}
\end{figure}

\paragraph{Concurrent connections}

\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-google-cdf.eps}
\caption{Normal Google Traffic}
\label{fig:len:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
\caption{Traffic Using meek}
\label{fig:len:meek}
\end{subfigure}

\caption{Connection lifetime distribution}
\label{fig:len}
\end{figure}

\paragraph{Connection lifetime}

\paragraph{Conclusion}

>>>>

The censor cannot sniff the content of communications or infer the existence of meek traffic 
from packet \emph{data}, 
since the communication is encrypted inside the TLS session, and we have devoted large efforts 
in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
the existence of meek traffic according to the \emph{meta-data}, i.e. traffic characteristics. 
We studied a collection of traffic characteristics and evaluated their possibilities of becoming
the censor's interest. Specifically, we considered three characteristics: 1) payload length of
TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime. To collect 
the traffic trace of meek, we browsed the Alexa top 500 websites sequentially using the Tor Browser Bundle
and dumped the traffic trace from 
the network interface. We ensured only the browser can successfully access the network by setting
up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
obtained a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. We also
specifically extracted the traffic between LBL and Google. Since the trace only has packet headers, we 
cannot extract the domain information. However, the \texttt{TXT} DNS records of the domain 
\texttt{\_netblocks.google.com} shows the IP address blocks that belongs to Google. Therefore, we 
determine whether a flow is from or to Google by examining the address in the IP header. For this
study we are only interested in Google traffic, because the censor will be mostly likely to compare
suspected meek traffic with normal Google traffic. This part of the trace is 312 MB in size.

@@

Recall that we use browsers to handle HTTPS connections for meek in order to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

These browser techniques improve performance, but also lead to unexpected risks. The censor may be aware of the 
deviation from the distribution of normal traffic. Additionally, the persistent connection itself can be a problem.
We thus investigated other related characteristics.

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth, angle=270]{figs/connections-google.eps}
\caption{Histogram of each user's connections in the 10-minute window}
\label{fig:connections}
\end{figure}
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figs/conns.eps}
\caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
\label{fig:conconns}
\end{figure}

\paragraph{Concurrent connections}
Figure \ref{fig:connections} shows how many HTTPS connections to Google did a user make 
during the 10-minute measurement window.
There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
50 connections to the Google frontend server, and most of the numbers concentrate on 1 ~ 10. This is not unexpected
because a typical pattern of using Google is using the Google search as a stepping stone for other websites.

We measure the number of concurrent HTTPS connections during the automated browsing of Alexa
top 500 sites using three platforms: Tor Browser Bundle, Safari + Firefox extension, and Safari + Chrome extension.
Figure \ref{fig:conconns} shows the number over time. We can see that most of the time
the browser has one HTTPS connection to Google. Sometimes the browser may have more than one connection
due to background activities such as statistics reporting. In all cases the number of connections is always 
less than 5. We can conclude that the number of concurrent connections does not show distinct characteristics, as 
a small number of connections can be considered as a normal behavior.

\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-google-cdf.eps}
\caption{Normal Google Traffic}
\label{fig:duration:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
\caption{Traffic Using meek (Notice the x-axis)}
\label{fig:duration:meek}
\end{subfigure}

\caption{Connection lifetime distribution}
\label{fig:duration}
\end{figure}

\paragraph{Connection lifetime}
We consider the connection lifetime as a potential weakness. Figure \ref{fig:duration:lbl} shows the 
connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
timeout of different browsers and web services. Another important observation is the concentration on 
durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
longer than 600 seconds.

The distribution of meek traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure \ref{fig:duration:meek}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user may already obtained the forbidden data she wants, or 
meek could simply restart a connection.

\paragraph{Conclusion} So far we have found two potential weaknesses: long-lived connections with bulk data transfer, 
and deviated distribution of packet sizes. To fundamentally fix these weaknesses we need to transform to the traffic into the normal-looking traffic. The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e. what
is the model of normal traffic, which is an open problem. However, the arm-race game is symmetric; since finding a right
model is a difficult task for us, it is also difficult for the censor. Therefore, the censor can only find ad-hoc 
characteristics to block forbidden traffic, which are relatively easy to defend against.
